---
title: "DEA"
output: html_notebook
---

 

```{r}
#install.packages('frontier')
#install.packages('xlsx')
#install.packages('lpSolve')
#install.packages('micEcon')
#install.packages("micEcon", repos="http://R-Forge.R-project.org")

#require
library('xlsx') # load xlsx package
library('lpSolve') # load lpSolve package
library('micEcon')
library('frontier')
library("plyr")
library( "plm" )
library("dplyr")
library("ggplot2")


```

## Load data from 2011 - 2020
### Excluded 2010 and 2021
### 2010 dataset and 2021 dataset sample are very small 41 Hospitals

```{r}

#load 2010 data only have 2k hospitals
#hospitals_2010 <- read.csv("C:\\Users\\K3NN0U\\Documents\\SCHOOL - Masters\\Spring 2022\\IDC6940\\hosp10-csv\\prds_hosp10_yr2010.csv")

#create data frame with 2010 data
#hospitals_2010 <- data.frame(hospitals_2010)
#hospitals_2010$YEAR <- 2010

#load 2011 data 
hospitals_2011 <- read.csv("C:\\Users\\K3NN0U\\Documents\\SCHOOL - Masters\\Spring 2022\\IDC6940\\hosp10-csv\\prds_hosp10_yr2011.csv")

#create data frame with 2011 data
hospitals_2011 <- data.frame(hospitals_2011)
hospitals_2011$YEAR <- 2011

#load 2012 data 
hospitals_2012 <- read.csv("C:\\Users\\K3NN0U\\Documents\\SCHOOL - Masters\\Spring 2022\\IDC6940\\hosp10-csv\\prds_hosp10_yr2012.csv")

#create data frame with 2012 data
hospitals_2012 <- data.frame(hospitals_2012)
hospitals_2012$YEAR <- 2012

#load 2013 data 
hospitals_2013 <- read.csv("C:\\Users\\K3NN0U\\Documents\\SCHOOL - Masters\\Spring 2022\\IDC6940\\hosp10-csv\\prds_hosp10_yr2013.csv")

#create data frame with 2013 data
hospitals_2013 <- data.frame(hospitals_2013)
hospitals_2013$YEAR <- 2013

#load 2014 data 
hospitals_2014 <- read.csv("C:\\Users\\K3NN0U\\Documents\\SCHOOL - Masters\\Spring 2022\\IDC6940\\hosp10-csv\\prds_hosp10_yr2014.csv")

#create data frame with 2014 data
hospitals_2014 <- data.frame(hospitals_2014)
hospitals_2014$YEAR <- 2014

#load 2015 data 
hospitals_2015 <- read.csv("C:\\Users\\K3NN0U\\Documents\\SCHOOL - Masters\\Spring 2022\\IDC6940\\hosp10-csv\\prds_hosp10_yr2015.csv")

#create data frame with 2015 data
hospitals_2015 <- data.frame(hospitals_2015)
hospitals_2015$YEAR <- 2015

#load 2016 data 
hospitals_2016 <- read.csv("C:\\Users\\K3NN0U\\Documents\\SCHOOL - Masters\\Spring 2022\\IDC6940\\hosp10-csv\\prds_hosp10_yr2016.csv")

#create data frame with 2016 data
hospitals_2016 <- data.frame(hospitals_2016)
hospitals_2016$YEAR <- 2016

#load 2017 data 
hospitals_2017 <- read.csv("C:\\Users\\K3NN0U\\Documents\\SCHOOL - Masters\\Spring 2022\\IDC6940\\hosp10-csv\\prds_hosp10_yr2017.csv")

#create data frame with 2017 data
hospitals_2017 <- data.frame(hospitals_2017)
hospitals_2017$YEAR <- 2017

#load 2018 data 
hospitals_2018 <- read.csv("C:\\Users\\K3NN0U\\Documents\\SCHOOL - Masters\\Spring 2022\\IDC6940\\hosp10-csv\\prds_hosp10_yr2018.csv")

#create data frame with 2018 data
hospitals_2018 <- data.frame(hospitals_2018)
hospitals_2018$YEAR <- 2018

#load 2019 data 
hospitals_2019 <- read.csv("C:\\Users\\K3NN0U\\Documents\\SCHOOL - Masters\\Spring 2022\\IDC6940\\hosp10-csv\\prds_hosp10_yr2019.csv")

#create data frame with 2019 data
hospitals_2019 <- data.frame(hospitals_2019)
hospitals_2019$YEAR <- 2019

#load 2020 data 
hospitals_2020 <- read.csv("C:\\Users\\K3NN0U\\Documents\\SCHOOL - Masters\\Spring 2022\\IDC6940\\hosp10-csv\\prds_hosp10_yr2020.csv")

#create data frame with 2020 data
hospitals_2020 <- data.frame(hospitals_2020)
hospitals_2020$YEAR <- 2020

#load 2021 data only have 41 hospitals 
#hospitals_2021 <- read.csv("C:\\Users\\K3NN0U\\Documents\\SCHOOL - Masters\\Spring 2022\\IDC6940\\hosp10-csv\\prds_hosp10_yr2021.csv")

#create data frame with 2021 data
#hospitals_2021 <- data.frame(hospitals_2021)
#hospitals_2021$YEAR <- 2021


#merge all years 

#final_hospitals <- rbind( hospitals_2010, hospitals_2011, hospitals_2012, hospitals_2013, hospitals_2014, hospitals_2015, hospitals_2016, hospitals_2017, hospitals_2018,hospitals_2019, hospitals_2020, hospitals_2021)

final_hospitals <- rbind( hospitals_2011, hospitals_2012, hospitals_2013, hospitals_2014, hospitals_2015, hospitals_2016, hospitals_2017, hospitals_2018,hospitals_2019, hospitals_2020)


final_hospitals


```


## COST ALLOCATION					
#### CMS COST form 2552-10 WORKSHEET B, PART I	

```{r}
hospitals_Admin_Cost <- final_hospitals[,c(
'YEAR','fi_creat_dt','fy_bgn_dt',	'fy_end_dt','prvdr_num','S2_1_C1_3', 'S2_1_C4_3', 'S2_1_C1_1', 'S2_1_C1_2' ,'S2_1_C2_2' ,'S2_1_C3_2','S2_1_C4_2','S2_1_C2_1',

'B_1_C0_1','B_1_C0_2','B_1_C0_3','B_1_C0_4','B_1_C0_5','B_1_C0_6','B_1_C0_7','B_1_C0_8','B_1_C0_9','B_1_C0_10','B_1_C0_11','B_1_C0_12','B_1_C0_13','B_1_C0_14','B_1_C0_15','B_1_C0_16','B_1_C0_17','B_1_C0_18','B_1_C0_19','B_1_C0_20','B_1_C0_21','B_1_C0_22','B_1_C0_23','B_1_C0_30','B_1_C0_31','B_1_C0_32','B_1_C0_33','B_1_C0_34','B_1_C0_35','B_1_C0_40','B_1_C0_41','B_1_C0_42','B_1_C0_4201','B_1_C0_43','B_1_C0_44','B_1_C0_45','B_1_C0_4501','B_1_C0_46','B_1_C0_50','B_1_C0_51','B_1_C0_52','B_1_C0_53','B_1_C0_54','B_1_C0_55','B_1_C0_56','B_1_C0_57','B_1_C0_58','B_1_C0_59','B_1_C0_60','B_1_C0_61','B_1_C0_62','B_1_C0_6250',

'B_1_C0_63','B_1_C0_64','B_1_C0_65','B_1_C0_66','B_1_C0_67','B_1_C0_68','B_1_C0_69','B_1_C0_70','B_1_C0_71','B_1_C0_72','B_1_C0_73','B_1_C0_74','B_1_C0_75','B_1_C0_76','B_1_C0_88','B_1_C0_89','B_1_C0_90','B_1_C0_91','B_1_C0_92','B_1_C0_9201','B_1_C0_93','B_1_C0_94','B_1_C0_95','B_1_C0_96','B_1_C0_97','B_1_C0_98','B_1_C0_99','B_1_C0_9910','B_1_C0_9920','B_1_C0_9930','B_1_C0_9940','B_1_C0_100','B_1_C0_101','B_1_C0_105','B_1_C0_106','B_1_C0_107','B_1_C0_108','B_1_C0_109','B_1_C0_110','B_1_C0_111','B_1_C0_112',

'B_1_C0_113','B_1_C0_114','B_1_C0_115','B_1_C0_116','B_1_C0_117','B_1_C0_190','B_1_C0_191','B_1_C0_192','B_1_C0_193','B_1_C0_194','B_1_C0_200',
'S2_1_C3_3','S3_1_C8_14'

)] 

# Rename column 
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "S2_1_C1_3"] <- "prvdr_name"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "S2_1_C4_3"] <- "prvdr_Type"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "S2_1_C1_1"] <- "prvdr_Address"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "S2_1_C1_2"] <- "prvdr_City"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "S2_1_C2_2"] <- "prvdr_State"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "S2_1_C3_2"] <- "prvdr_Zip_Code"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "S2_1_C4_2"] <- "prvdr_County"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "S2_1_C2_1"] <- "prvdr_PO_Box"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "S2_1_C3_3"] <- "prvdr_MSA_CBSA"


names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_1"] <- "New Capital Buildings and Fixtures"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_2"] <- "New Capital Equipment"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_3"] <- "Other Capital"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_4"] <- "Employee Benefits"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_5"] <- "Administrative_and_General"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_6"] <- "Maintenance and Repairs"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_7"] <- "Operation of Plant"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_8"] <- "Laundry and Linen Service"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_9"] <- "Housekeeping"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_10"] <- "Dietary"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_11"] <- "Cafeteria"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_12"] <- "Maintenance of Personnel"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_13"] <- "Nursing Administration"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_14"] <- "Central Services and Supply"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_15"] <- "Pharmacy"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_16"] <- "Medical Records and Medical Rec. Library"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_17"] <- "Social Service"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_18"] <- "Other General Service"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_19"] <- "Nonphysician Anesthetists"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_20"] <- "Nursing School"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_21"] <- "Interns & Res Salary and Fringe Benefits"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_22"] <- "Interns & Res Other Program Costs"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_23"] <- "Paramedical Education"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_30"] <- "Adults and Pediatrics"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_31"] <- "Intensive Care Unit"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_32"] <- "Coronary Care Unit"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_33"] <- "Burn Intensive Care Unit"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_34"] <- "Surgical Intensive Care Unit"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_35"] <- "Other Special Care Unit"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_40"] <- "Subprovider-IPF"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_41"] <- "Subprovider-IRF"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_42"] <- "Subprovider I"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_4201"] <- "Subprovider II"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_43"] <- "Nursery"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_44"] <- "SNF"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_45"] <- "NF"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_4501"] <- "ICF"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_46"] <- "OLTC"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_50"] <- "Operating Room"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_51"] <- "Recovery Room"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_52"] <- "Delivery Room and Labor Room"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_53"] <- "Anesthesiology"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_54"] <- "Radiology-Diagnostic"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_55"] <- "Radiology-Therapeutic"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_56"] <- "Radioisotope"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_57"] <- "CT Scan"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_58"] <- "MRI"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_59"] <- "Cardiac Catheterization"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_60"] <- "Laboratory"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_61"] <- "PBP Clinical Lab Services Program Only"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_62"] <- "Whole Blood & Packed Red Blood Cells"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_6250"] <- "Blood Clotting Factors for Hemoph."

names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_63"] <- "Blood Storing, Processing, Trans"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_64"] <- "Intravenous Therapy"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_65"] <- "Respiratory Therapy"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_66"] <- "Physical Therapy"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_67"] <- "Occupational Therapy"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_68"] <- "Speech Pathology"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_69"] <- "Electrocardiology"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_70"] <- "Electroencephalography"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_71"] <- "Medical Supplies Charged to Patients"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_72"] <- "Impl. Dev. Charged to Patients "
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_73"] <- "Drugs Charged to Patients"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_74"] <- "Renal Dialysis"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_75"] <- "ASC (Non Distinct Part)"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_76"] <- "Other Ancillary"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_88"] <- "RHC"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_89"] <- "FQHC"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_90"] <- "Clinic"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_91"] <- "Emergency"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_92"] <- "Observation Beds (non Distinct Unit)"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_9201"] <- "Observation Beds (Distinct Unit)"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_93"] <- "Other Outpatient Services"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_94"] <- "Home Program Dialysis"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_95"] <- "Ambulance Services"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_96"] <- "Durable Medical Equipment Rented"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_97"] <- "Durable Medical Equipment Sold"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_98"] <- "Other Reimbursable"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_99"] <- "CMHC"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_9910"] <- "CORF"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_9920"] <- "OPT"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_9930"] <- "OOT"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_9940"] <- "OSP"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_100"] <- "Int & Res (non approved teaching program"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_101"] <- "HHA"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_105"] <- "Kidney Acquisition"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_106"] <- "Heart Acquisition"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_107"] <- "Liver Acquisition"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_108"] <- "Lung  Acquisition"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_109"] <- "Pancreas Acquisition"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_110"] <- "Intestinal Acquisition"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_111"] <- "Islet Acquisition"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_112"] <- "Other Organ Acquisition"

names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_113"] <- "Interest Expense"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_114"] <- "Utilization Review SNF"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_115"] <- "ASC (Distinct Part)"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_116"] <- "Hospice"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_117"] <- "Other Special Purpose"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_190"] <- "Gift, Flower, Coffee Shop, Canteen"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_191"] <- "Research"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_192"] <- "Physicians Private Office"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_193"] <- "Nonpaid Workers"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_194"] <- "Other Nonreimbursable"
names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "B_1_C0_200"] <- "Total"

names(hospitals_Admin_Cost)[names(hospitals_Admin_Cost) == "S3_1_C8_14"] <- "Total_Inpatient_outpatient_Visits"




hospitals_Admin_Cost

```

## The number listed best corresponds with the type of Hospitals 
### 1 = General Short Term, 
### 2 = General Long Term, 
### 3 = Cancer, 
### 4 = Psychiatric, 
### 5 = Rehabilitation, 
### 6 = Religious Non-Medical Health Care Institution, 
### 7 = Children, 
### 8 = Alcohol and Drug, 
### 9 = Other
### 10 = Extended Neoplastic Disease Care
### 11 = Indian Health Service 

```{r}

HospitalSample <- ddply(hospitals_Admin_Cost, .(hospitals_Admin_Cost$prvdr_num, hospitals_Admin_Cost$YEAR), nrow)
names(HospitalSample) <- c("prvdr_num", "Year", "Freq")


```

## Hospitals reports from 2011 - 2020
```{r}


HospitalSample <- HospitalSample %>%
    group_by(prvdr_num) %>%
    mutate(group_sum = sum(Freq))

HospitalSample
```

```{r}

HospitalSample <- HospitalSample[!(HospitalSample$group_sum <  10),]
HospitalSample

```
## Hospitals reports By Year

```{r}

Hospitalyear <- aggregate(cbind(count = prvdr_num) ~ Year, 
          data = HospitalSample, 
          FUN = function(x){NROW(x)})

Hospitalyear
```
## Hospitals Type reports By Year
```{r}

Hospitaltype <- ddply(hospitals_Admin_Cost, .(hospitals_Admin_Cost$prvdr_Type, hospitals_Admin_Cost$YEAR), nrow)
names(Hospitaltype) <- c("prvdr_Type", "Year", "Freq")

Hospitaltype

```

## Hospitals Administrative cost Total reports from 2011 - 2020
```{r}
boxplot(Total ~ prvdr_Type , data = hospitals_Admin_Cost, xlab = "Hospital Type",
   ylab = "Administrative Cost", main = "Administrative Cost Charges Data" , outline=TRUE)

boxplot(Total ~ prvdr_Type , data = hospitals_Admin_Cost, xlab = "Hospital Type",
   ylab = "Administrative Cost", main = "Administrative Cost Charges Data" , outline=FALSE)

ggplot(hospitals_Admin_Cost, aes(x=factor(prvdr_Type), y=Total , fill=factor(prvdr_Type))) +
  geom_bar(stat="identity")+
  #geom_text(aes(label=Administrative_and_General), vjust=1, size=2.5)+
  labs(y= "Administrative Cost", x = "Hospital Type",fill = "Hospital Type")+
  #coord_flip(xlim = NULL, ylim = NULL, expand = TRUE, clip = "on")+
  theme_minimal()

```
### Hospital Data Summary from 2011 - 2020


```{r}
summary(hospitals_Admin_Cost)

```

```{r}

#The input variable is the OPEX located at second column of the data matrix. 
#The output variables are at columns 3 (NETWORK), 4 (MWH) and 5 (CUSTOMERS) 
#of the data matrix. 
#The selection of inputs and outputs variables can be done by the following 
#commands:
hospitalsampledata <- head(hospitals_Admin_Cost, 10)

inputs <- data.frame(hospitalsampledata['Total'])  # input variable at second column of the data matrix
#inputs <- head(inputs, 10) 
inputs

outputs <- data.frame(hospitalsampledata['Total_Inpatient_outpatient_Visits'])  # output variables 
#outputs <- head(outputs, 10)
outputs

N <- dim(hospitalsampledata)[1] # the number of DMUs is equal to number of rows of data matrix 
s <- dim(inputs)[2] # number of input variables, in this case s = 1
m <- dim(outputs)[2] # number of output variables, in this case m = 1

N
s
m

```



```{r}

#CRS Model

f.rhs <- c(rep(0,1,N),1) 
f.dir <- c(rep("<=",1,N),"=") 
aux <- cbind(-1*inputs,outputs)

#loop of N DMUs

for (i in 1:N) {
 f.obj <- c(0*rep(1,s),as.numeric(outputs[i,]))
 f.con <- rbind(aux ,c(as.numeric(inputs[i,]), rep(0,1,m))) 
 results <- lp ("max",as.numeric(f.obj), f.con, f.dir, f.rhs,scale=0, compute.sens=TRUE)
 if (i==1) {
 weights <- results$solution
 effcrs <- results$objval
 lambdas <- results$duals[seq(1,N)] 
 } else {
 weights <- rbind(weights, results$solution)
 effcrs <- rbind(effcrs , results$objval)
 lambdas <- rbind(lambdas, results$duals[seq(1,N)] )
 }
}


```



```{r}

# merge the efficiency and multipliers
spreadsheet <- cbind(effcrs,weights)

hospitalname <- hospitalsampledata  
# assign the Hospital’ names to the spreadsheet rows
rownames(spreadsheet) <- hospitalname[,6]  #['prvdr_name']

# assign the variables names to the spreadsheet columns
colnames(spreadsheet) <- c('efficiency',names(inputs),names(outputs)) 

spreadsheet
           
```


```{r}
# duals variables
spreadsheet<-lambdas

# assign the Hospital’ names to the spreadsheet rows and columns
rownames(spreadsheet)<- hospitalname[,6]  #['prvdr_name']
colnames(spreadsheet)<- hospitalname[,6]  #['prvdr_name']

spreadsheet



```

```{r}

# VIsualisation of hospital Efficiency 

par(mar=c(10,5,1,10),xpd=TRUE) # set plot margin
palette(gray(0:8 / 8)) # set color palette
virtual<-weights[,(s+1):(s+m)]*outputs # virtual outputs
rownames(virtual)<-hospitalname[,6] # assign Hospital’ names to the rows of the object virtual
barplot(t(virtual),col=palette()[c(1,4,7)],ylab="Efficiency",cex.axis=1,cex.lab=1,cex.names=1,las=3)
legend("topright",inset=c(-0.45,0),colnames(virtual),fill=palette()[c(1,4,7)],bty="n") # add legend

```

```{r}

# VIsualisation of hospital Efficiency 

par(mar=c(10,5,1,1)) # set plot margin
palette(gray(0:8 / 8)) # set color palette
rownames(lambdas)<-hospitalname[,6] # assigns Hospital’ names to the rows of duals variables matrix
colnames(lambdas)<-hospitalname[,6] # assigns Hospital’ names to the colimns of duals variables matrix
peer<-which(apply(lambdas,2,sum)>0) # identifies reference units (efficiency units)
barplot(t(lambdas[,peer]),col=palette()[c(1,4,7)],cex.axis=1,cex.lab=1,cex.names=1,las=3)
legend("topright",colnames(lambdas)[peer],fill=palette()[c(1,4,7)],bty="n") # add legend

```


```{r}
#The difference between CRS and VRS models resides in the unconstrained variable u0
 
#This variable can be modeled by the difference of two non negative variables (u0 = u+ - u- , where u+ >= 0 and u- >=0)

#VRS Model

f.rhs <- c(rep(0,1,N),1) 
f.dir<-c(rep("<=",1,N), "=") 
aux <- cbind(-1*inputs,outputs,1,-1) 
for (i in 1:N) {
 f.obj<-c(rep(0,1,s),as.numeric(outputs[i,]),1,-1) # 1 and -1 represents u+ - u-
 f.con <- rbind(aux,c(as.numeric(inputs[i,]),rep(0,1,m),0,0))
 results <- lp ("max",as.numeric(f.obj), f.con, f.dir, f.rhs,scale=1, compute.sens=TRUE)
 multipliers <- results$solution
 u0 <- multipliers[s+m+1]-multipliers[s+m+2] 
 if (i==1) {
 weights <- c(multipliers[seq(1,s+m)],u0)
 effvrs <- results$objval
 lambdas <- results$duals[seq(1,N)] 
 } else {
 weights<-rbind(weights,c(multipliers[seq(1,s+m)],u0))
 effvrs <- rbind(effvrs , results$objval)
 lambdas <- rbind(lambdas,results$duals[seq(1,N)])
 }
} 


```

```{r}
spreadsheet<-cbind(effvrs,weights) # merge de results
rownames(spreadsheet)<- hospitalname[,6] # assign the hospital’ names to spreadsheet rows 
colnames(spreadsheet)<-c('efficiency',names(inputs), names(outputs),'u0')

spreadsheet


```

```{r}

# Visualisation 

par(mar=c(10,5,1, 8),xpd=TRUE) # set plot margin
scale <- effcrs/effvrs
spreadsheet <- cbind(effcrs,effvrs,scale)
rownames(spreadsheet) <- hospitalname[,6] # assign the hospital’ names to spreadsheet rows
colnames(spreadsheet) <- c("CRS","VRS","SE")
barplot(t(spreadsheet), 
col=palette()[c(1,4,7)],ylab="Efficiency",beside=TRUE,cex.axis=1,cex.lab=1,cex.names=1,las=3)
legend("topright",inset=c(-0.2,0),colnames(spreadsheet),fill=palette()[c(1,4,7)],bty="n") # add legend

```

```{r}
#References
#Angulo-Meza, L.; Estellita Lins, M.P. Review of methods for increasing discrimination in data
#envelopment analysis, Annals of Operational Research, 116, pp. 225-242, 2002.
#Banker, R.D.; Charnes, A. & Cooper, W.W. Some models for estimating technical and scale
#inefficiencies in data envelopment analysis. Management Science, 30, 1078-1092, 1984.
#Bogetoft, P., Otto, L. Benchmarking with DEA, SFA and R, Springer Science, 2011.
#Charnes, A.; Cooper, W.W. & Rhodes, E. Measuring the Efficiency of Decision
#Making Units. European Journal of Operational Research, 2, 1978.
#Coelli, T.J.; Rao, D.S.P.; O’Donnell, C.J.; Battese, G.E. An introduction to efficiency and productivity
#analysis, Springer, 2005.
#Cook, W.D.; Seiford, L.M. Data Envelopment Analysis (DEA) – Thirty years on, European Journal of
#Operational Research, 192, pp. 1-17, 2009.
#Cooper, W.W.; Seiford, L.M.; Tone, K. Data Envelopment Analysis: A comprehensive text with
#models, applications, references and DEA-Solver Software, Kluwer Academic Publishers, 2002.
#El-Mahgary, S.; Lahdelma, R. Data Envelopment Analysis: Visualizing the results, European
#Journal of Operational Research, 85, pp. 700-710, 1995.
#Guo, P.; Tanaka, H. Fuzzy DEA: a perceptual evaluation method, Fuzzy Sets and Systems, 119, pp.
#149-160, 2001.
#Ragsdale, C.T. Spreadsheet modeling & decision analysis: a practical introduction to management
#science. 4.ed. Thomson South-Western, 2004.
#R Development Core Team R: A language and environment for statistical computing. R Foundation
#for Statistical Computing, Vienna, Austria. URL http://www.R-project.org/, 2011.
#Verzani, J. Using R for introductory statistics, Chapman & Hall/ CRC Press, 2005

```


```{r}

#Extract the coefficients from stochastic frontier models returned by frontier.

sfaResult <- sfa( log( Total_Inpatient_outpatient_Visits ) ~ log(Total) ,
data = hospitalsampledata )
coef( sfaResult, which = "ols" )
coef( sfaResult, which = "grid" )
coef( sfaResult )

```



```{r}


# Error Components Frontier (Battese & Coelli 1992), no time effect
hospital <- sfa( log( Total_Inpatient_outpatient_Visits ) ~ log( Total ) ,
data = hospitalsampledata )
efficiencies( hospital )
hospitalsampledata$efficiencies <- efficiencies( hospital, asInData = TRUE )

# efficiency of an 'average' Hospital
efficiencies( hospital,
newdata = data.frame( t( colMeans( hospitalsampledata[ , -c(1,2,3,4,5,6,7,8,9,10,11,12,13) ] ) ) ) )

# Error Components Frontier (Battese & Coelli 1992), with time effect
hospital <- sfa( log( Total_Inpatient_outpatient_Visits ) ~ log( Total ) ,
data = hospitalsampledata, timeEffect = TRUE )
efficiencies( hospital )
hospitalsampledata$efficienciesTime <- efficiencies( hospital, asInData = TRUE)

summary(hospital )

```



```

